# Model

## General

[SOTA Results](https://paperswithcode.com/sota)

cohort analysis, Transfer learning, cox proportional hazards, youden's j, Multiple Correspondence Analysis. platt scaling, generalized low rank models, conditional random field, linear probability model

toolbox: classic ml, bayesian ml, abm, rl, ga & gp, es

"No Free Lunch" theorem: no single classifier works best across all possible scenarios

Always set the seed

natural log goes from unit change to percentage change

Simulated Annealing: Gradient descent extension

hierarchical clustering: ward

hamming loss: multilabel and multiclass classification

Sequence mining Algorithms: spade, gsp, freespan; hmmlearn 

Network models: graphical lasso, ising model, granger causality test, network hypothesis testing, bayesian networks

sequential data: rnn, lstm, hidden markov models & conditional random fields

fowles-mallows score for clustering when ground truth is known

Clustering: [Comparison](http://scikit-learn.org/stable/modules/clustering.html#clustering) | [Rules](https://twitter.com/thomaswdinsmore/status/965223193043718145)

[Network Playground](https://mikedombo.github.io/graphPlayground/#)

train & dev set error: low-high = high variance, high-high = high bias, high-high = high bias and variance, low-low = low bias and variance

Opposite the other algorithms, increasing n in KNN means less overfitting.

KNN doesn't easily extrapolate as linear regression.

Linear Regression better than KNN: space to store model, time to query

KNN better than LinReg: compute time to train, ease to add new data

As m increases, AdaBoost tries to assign more and more specific data points to subsequent learners, trying to model all the difficult examples. Thus, compared to simple bagging, it may result in more over-fitting.

[SNAP Network Library](https://snap.stanford.edu/snappy/index.html)

* The ML Fine Print: Three basic assumptions: 1) We draw examples independently and identically (i.i.d.) at random from the distribution, 2) The distribution is stationary: It doesn't change over time, 3) We always pull from the same distribution: Including training, validation, and test sets. In practice, we sometimes violate these assumptions. For example: 1) Consider a model that chooses ads to display. The i.i.d. assumption would be violated if the model bases its choice of ads, in part, on what ads the user has previously seen. 2) Consider a data set that contains retail sales information for a year. User's purchases change seasonally, which would violate stationarity. When we know that any of the preceding three basic assumptions are violated, we must pay careful attention to metrics.

* empirical risk minimization: In supervised learning, a machine learning algorithm builds a model by examining many examples and attempting to find a model that minimizes loss.

* Loss is the penalty for a bad prediction. That is, loss is a number indicating how bad the model's prediction was on a single example. If the model's prediction is perfect, the loss is zero; otherwise, the loss is greater. 

* If a model suffers from overfitting, we also say that the model has a high variance, which can be caused by having too many parameters that lead to a model that is too complex given the underlying data. Similarly, our model can also suffer from underfitting (high bias), which means that our model is not complex enough to capture the pattern in the training data well and therefore also suffers from low performance on unseen data.

* "Product classification is an example of multicategory or multinomial classification. Most classification problems and most classification algorithms are specialized for two-category, or binomial, classification. There are tricks to using binary classifiers to solve multicategory problems (for example, building one classifier for each category, called a “one versus rest” classifier). But in most cases it’s worth the effort to find a suitable multiple-category implementation, as they tend to work better than multiple binary classifiers (for example, using the package mlogit instead of the base method glm() for logistic regression)."

With large data we can to the train x dev x test split of 98 x 1 x 1.

Bayes optimal error: Aim for this. The difference b/w training error and BOE is the avoidable bias.

new data degrades your model. what should you do? Use the data you have to define a new evaluation metric (using a new dev/test set) taking into account the new species, and use that to drive further progress for your team.

because even though you have higher overall accuracy, you have more false negatives (failing to raise an alarm when a bird is in the air). What should you do? Rethink the appropriate metric for this task, and ask your team to tune to the new metric.

* So, if your problem involves kind of searching a needle in the haystack when for ex: the positive class samples are very rare compared to the negative classes, use a precision recall curve. Otherwise use a ROC curve because a ROC curve remains the same regardless of the baseline prior probability of your positive class (the important rare class).

* Parametric: Model has a function shape and form, Model is trained/fit using training data to determine parameter values, reduces the problem of training a model down to training a set of parameter values, Examples: linear regression. Non-Parametric: No assumption about model form is made, Example: KNN

https://scikit-learn.org/stable/modules/classes.html#module-sklearn.semi_supervised

## Model

### General

Semi-supervised: active learning | [Auto Labeling](https://blog.fastforwardlabs.com/2018/09/28/snorkel-rapid-training-data-creation-with-weak-supervision.html)

https://machinelearningmastery.com/

Active Learning: Finding the optimal data to manually label

[Python Distributed](https://speakerdeck.com/seanoc/a-tour-of-large-scale-data-analysis-tools-in-python)

[SklearnDsitributed ](https://alexperrier.github.io/jekyll/update/2016/03/16/out-of-core-scikit-boston-meetup.html#/)

[Spark Hub](https://sparkhub.databricks.com/)

Interactive ML: [1](https://channel9.msdn.com/Events/useR-international-R-User-conference/useR2016/Interactive-Naive-Bayes-using-Shiny-Text-Retrieval-Classification-Quantification) | [2](https://nuit-blanche.blogspot.com/2017/02/saturday-morning-videos-interactive.html)
  
[Online Learning](http://scikit-learn.org/stable/modules/generated/sklearn.linear_model.PassiveAggressiveRegressor.html)

[ML APIs](http://www.kdnuggets.com/2015/12/machine-learning-data-science-apis.html)

[Auto Optimization](https://sigopt.com/)

[Google ML Glossary](https://developers.google.com/machine-learning/glossary/)

[Apache System ML](https://systemml.apache.org)

[Learning Curves](http://www.ritchieng.com/machinelearning-learning-curve/)

[Gaussian Processes](http://scikit-learn.org/stable/modules/gaussian_process.html)

[Debugging ML](http://nlpers.blogspot.com/2016/08/debugging-machine-learning.html)

http://gael-varoquaux.info/interpreting_ml_tuto/index.html

[LM Model Diagnostics](http://mpastell.com/2013/04/19/python_regression/)

[Gain Curve](https://www.rdocumentation.org/packages/WVPlots/versions/0.2.6/topics/GainCurvePlot)

[Metrics](https://www.analyticsvidhya.com/blog/2016/02/7-important-model-evaluation-error-metrics/)

[Choosing A Classifier](http://blog.echen.me/2011/04/27/choosing-a-machine-learning-classifier/)

[LOOCV Perils](http://www.russpoldrack.org/2012/12/the-perils-of-leave-one-out.html)

[Model Evaluations](http://www.win-vector.com/blog/2016/12/be-careful-evaluating-model-predictions/)

[Model Evaluation](http://blog.dato.com/how-to-evaluate-machine-learning-models-part-1-orientation)

CV Mistakes: [1](http://betatim.github.io/posts/cross-validation-gone-wrong/) |  [2](http://www.alfredo.motta.name/cross-validation-done-wrong/) |  [3](http://robjhyndman.com/hyndsight/crossvalidation/)

[Partial Dependence Plots](https://cran.r-project.org/web/packages/pdp/pdp.pdf)

https://pair-code.github.io/what-if-tool/

permutation importance (eli5)

https://pbiecek.github.io/breakDown/

[Break Down Plots](https://cran.r-project.org/web/packages/breakDown/index.html)
</div>
<br/>

http://clus.sourceforge.net/doku.php

https://scikit-optimize.github.io/notebooks/sklearn-gridsearchcv-replacement.html

https://scikit-optimize.github.io/notebooks/hyperparameter-optimization.html

[sklearn metrics](http://scikit-learn.org/stable/modules/model_evaluation.html#function-for-prediction-error-metrics)

[Algorithm Comparison](https://docs.google.com/spreadsheets/d/16i47Wmjpj8k-mFRk-NnXXU5tmSQz8h37YxluDV8Zy9U/edit#gid=0)

[Regression Effects Lib](https://www.rdocumentation.org/packages/yhat/versions/2.0-0)

anomalies: [skl](http://scikit-learn.org/stable/modules/outlier_detection.html) | [R](https://business-science.github.io/anomalize/)

lightgbm: [tuning](https://medium.com/@pushkarmandot/https-medium-com-pushkarmandot-what-is-lightgbm-how-to-implement-it-how-to-fine-tune-the-parameters-60347819b7fc) | [ex](https://www.kaggle.com/ezietsman/simple-python-lightgbm-example)

[Tree Analysis Viz](http://etetoolkit.org/)

unbalanced classes: [R](https://cran.r-project.org/web/packages/imbalance/index.html) | [Py](http://contrib.scikit-learn.org/imbalanced-learn/stable/)

[Interactive ML](http://www.creativeai.net/posts/eivW6BvrrpyPf282d/interactive-machine-learning-an-overview-in-5-videos)

Ensembles: [General](http://mlwave.com/kaggle-ensembling-guide/) | [caret](http://amunategui.github.io/blending-models/) | [skl](https://www.toptal.com/machine-learning/ensemble-methods-machine-learning) | [1](http://blog.kaggle.com/2016/12/27/a-kagglers-guide-to-model-stacking-in-practice/) | [2](http://blog.kaggle.com/2017/06/15/stacking-made-easy-an-introduction-to-stacknet-by-competitions-grandmaster-marios-michailidis-kazanova/)

Multilevel regression and post stratification

Mixed Models / multilevel / hierarchical / mixed-effects models

Multiple Factor Analysis: FactoMineR

Functional PCA

LMM: [1](http://edwardlib.org/tutorials/linear-mixed-effects-models) | [2](https://ourcodingclub.github.io/2017/03/15/mixed-models.html)

Sklearn Model Selection: [1](http://scikit-learn.org/stable/modules/generated/sklearn.model_selection.GroupKFold.html) | [2](http://scikit-learn.org/stable/modules/generated/sklearn.model_selection.LeaveOneGroupOut.html) | [3](http://scikit-learn.org/stable/modules/generated/sklearn.model_selection.LeavePGroupsOut.html)

[Annotation](https://explosion.ai/blog/prodigy-annotation-tool-active-learning)

[Mixed Data Clustering](https://www.r-bloggers.com/clustering-mixed-data-types-in-r/)

[Dimensionality Reduction Techniques](https://colah.github.io/posts/2014-10-Visualizing-MNIST/)

[Unsupervised Learning Sklearn](http://opensource.datacratic.com/mtlpy50/)

[Info Maximization](http://www.inference.vc/unsupervised-learning-by-predicting-noise-an-information-maximization-view-2/)

[K-Means On MNIST](http://johnloeber.com/docs/kmeans.html)

tsne: [1](http://distill.pub/2016/misread-tsne/) | [2](https://lvdmaaten.github.io/tsne/) | [3](https://index.pocketcluster.io/harveyslash-tsne-embedding-visualisation.html)

### Model Selection/Evaluation

* **The Coefficient of Unalikeability**: Unalikeability is defined as how often observations differ from one another. It varies from 0 to 1. The higher the value, the more unalike the data are.

* Make sure that your test set meets the following two conditions: 1) Is large enough to yield statistically meaningful results, 2) Is representative of the data set as a whole. In other words, don't pick a test set with different characteristics than the training set.

* Linear SVM often outperforms logistic regression and is explainable as well.

* However, the problem with cross-validation is that it is rarely applicable to real world problems, for all the reasons described in the above sections. Cross-validation only works in the same cases where you can randomly shuffle your data to choose a validation set.

* If the performance of a classification model on the test set (out-of-sample) error is poor, you can't just re-calibrate your model parameters to achieve a better model. This is cheating.

* When the classes are well-separated, the parameter estimates for the logistic regression model are surprisingly unstable. Linear discriminant analysis does not suffer from this problem. If n is small and the distribution of the predictors X is approximately normal in each of the classes, the linear discriminant model is again more stable than the logistic regression model.

* Roughly speaking, LDA tends to be a better bet than QDA if there are relatively few training observations and so reducing variance is crucial. In contrast, QDA is recommended if the training set is very large, so that the variance of the classifier is not a major concern, or if the assumption of a common covariance matrix for the K classes is clearly untenable.

* Two features interact if the effect on the prediction of one feature depends on the value of the other feature

* Warning PolynomialFeatures(degree=d) transforms an array containing n features into an array containing  features, where n! is the factorial of n, equal to 1 × 2 × 3 × ⋯ × n. Beware of the combinatorial explosion of the number of features!

* It appears that each feature has modestly improved our model. There are certainly more features that we could add to our model. For example, we could add the day of the week and the hour of the posting, we could determine if the article is a listicle by running a regex on the headline, or we could examine the sentiment of each article. This only begins to touch on the features that could be important to model virality. We would certainly need to go much further to continue reducing the error in our model.

* Suppose Fixitol reduces symptoms by 20% over a placebo, but the trial you’re using to test it is too small to have adequate statistical power to detect this difference reliably. We know that small trials tend to have varying results; it’s easy to get 10 lucky patients who have shorter colds than usual but much harder to get 10,000 who all do.

* As I mentioned earlier, one drawback of the Bonferroni correction is that it greatly decreases the statistical power of your experiments, making it more likely that you’ll miss true effects. More sophisticated procedures than Bonferroni correction exist, ones with less of an impact on statistical power, but even these are not magic bullets. Worse, they don’t spare you from the base rate fallacy. You can still be misled by your p threshold and falsely claim there’s “only a 5% chance I’m wrong.” Procedures like the Bonferroni correction only help you eliminate some false positives.

* In step 1, we find where missing values are located. The md.pattern() function from the mice package is a really useful function. It gives you a clear view of where missing values are located, helping you in decisions regarding exclusions or substitution. You can refer to the next recipe for missing value substitution.

* Another possible indication of collinearity in the inputs is seeing coefficients with an unexpected sign: for example, seeing that income is negatively correlated with years in the workforce.

* The overall model can still predict income quite well, even when the inputs are correlated; it just can’t determine which variable deserves the credit for the prediction. Using regularization (especially ridge regression as found in lm.ridge() in the package MASS) is helpful in collinear situations (we prefer it to “x-alone” variable preprocessing, such as principal components analysis). If you want to use the coefficient values as advice as well as to make good predictions.

* The degrees of freedom is thought of as the number of training data rows you have after correcting for the number of coefficients you tried to solve for. You want the degrees of freedom to be large compared to the number of coefficients fit to avoid overfitting.

* The probable reason for nonconvergence is separation or quasi-separation: one of the model variables or some combination of the model variables predicts the outcome perfectly for at least a subset of the training data. You’d think this would be a good thing, but ironically logistic regression fails when the variables are too powerful.

* For categorical variables (male/female, or small/medium/large), you can define the distance as 0 if two points are in the same category, and 1 otherwise. If all the variables are categorical, then you can use Hamming distance, which counts the number of mismatches.

* Your next step is to select a performance measure. A typical performance measure for regression problems is the Root Mean Square Error (RMSE). It measures the standard deviation of the errors the system makes in its predictions.

* You should save every model you experiment with, so you can come back easily to any model you want. Make sure you save both the hyperparameters and the trained parameters, as well as the cross-validation scores and perhaps the actual predictions as well. This will allow you to easily compare scores across model types, and compare the types of errors they make. You can easily save Scikit-Learn models by using Python’s pickle module, or using sklearn.externals.joblib, which is more efficient at serializing large NumPy arrays.

* If all classifiers are able to estimate class probabilities (i.e., they have a predict_proba() method), then you can tell Scikit-Learn to predict the class with the highest class probability, averaged over all the individual classifiers. This is called soft voting. It often achieves higher performance than hard voting because it gives more weight to highly confident votes. All you need to do is replace voting="hard" with voting="soft" and ensure that all classifiers can estimate class probabilities.

* The standard value for k in k-fold cross-validation is 10, which is typically a reasonable choice for most applications. However, if we are working with relatively small training sets, it can be useful to increase the number of folds. If we increase the value of k, more training data will be used in each iteration, which results in a lower bias towards estimating the generalization performance by averaging the individual model estimates. However, large values of k will also increase the runtime of the cross-validation algorithm and yield estimates with higher variance since the training folds will be more similar to each other. On the other hand, if we are working with large datasets, we can choose a smaller value for k.

* Distance Metrics: Hamming distance for categorical variables, Cosine distance for text data, Gower distance for categorical data

* AIC x BIC: Explanatory power x Parsimonious

* Bias is how far offon the average the model is from the truth. Variance is how much the estimate varies about its average. With low model complexity bias is high because predictions are more likely to stray from the truth, and variance is low because there are only few parameters being fit. With high model complexity bias is low because the model can adapt to more subtleties in the data, and variance is high because we have more parameters to estimate from the same amount of data.

* The mean of highly correlated quantities has higher variance than the mean of uncorrelated quantities. The smaller the number of folds, the more biased the error estimates (they will be biased to be conservative indicating higher error than there is in reality) but the less variable they will be. On the extreme end you can have one fold for each data point which is known as Leave-One-Out-Cross-Validation. In this case, your error estimate is essentially unbiased but it could potentially have high variance. 

* LDA vs Logistic Regression: When the classes are well-separated parameters of logistic regression are unstable and LDA doesn't have this problem. If the distribution of X is approximately normal then LDA is more stable again. LDA doesn't need to fit multiple models for multiclass classification.

* SVM vs Logistic Regression: SVM is likely to overfit the data and can dominated LR on the training set. Kernel method makes SVM more flexible.

* Decision Tree vs Linear Model: Tree has non-linear boundary, selects important features, easier to intepret but unstable especially for small data.

* Naive Bayes vs LDA: Both use Bayes theorem, both assume gaussian distribution, but LDA takes care of the correlations. LDA might out-perform Naive Bayes when the features are highly correlated. 

* KNN vs Other Classification Methods: KNN is completely non-parametic, doesn't tell which features are important. Dominates LDA and Logistic Regression when the decision boundary is highly non-linear.

* When building, testing, and validating a suite of models, the optimal model (i.e., the optimal point in the ROC curve) is the spot where the overall accuracy of the model is essentially unchanged as we make small adjustments in the choice of model. That is to say, the change (from one model to the next) in the model’s precision (specificity) is exactly offset by the change in the model’s recall (sensitivity). Consequently, allowing for some imperfection, where the false positive rate and the false negative rate are in proper balance (so that neither one has too great of an impact on the overall accuracy and effectiveness of the model), is good fruit from your big data labors. The metric I used to guide my cross-validation is the F-score. This is a good metric when we have a lot more samples from one category than from the other categories.

* The cost of the holdout method comes in the amount of data that is removed from the model training process. For instance, in the illustrative example here, we removed 30% of our data. This means that our model is trained on a smaller data set and its error is likely to be higher than if we trained it on the full data set. The standard procedure in this case is to report your error using the holdout set, and then train a final model using all your data.

* A metric that minimizes false positives, by rarely flagging players and teams that fail to achieve the desired outcome, is specific. A metric that minimizes false negatives, by rarely failing to flag players and teams that achieve the desired outcome, is sensitive.

* Sometimes it may be more useful to report the coefficient of determination (), which can be understood as a standardized version of the MSE, for better interpretability of the model performance. In other words,  is the fraction of response variance that is captured by the model. The  value is defined as follows:Here, SSE is the sum of squared errors and SST is the total sum of squares , or in other words, it is simply the variance of the response.

* Most people start working with data from exactly the wrong end. They begin with a data set, then apply their favorite tools and techniques to it. The result is narrow questions and shallow arguments. Starting with data, without first doing a lot of thinking, without having any structure, is a short road to simple questions and unsurprising results. We don’t want unsurprising - we want knowledge.

* Remember that the positive class in scikit-learn is the class that is labeled as class 1. If we want to specify a different positive label, we can construct our own scorer via the make_scorer function, which we can then directly provide as an argument to the scoring parameter in GridSearchCV

* While the weighted macro-average is the default for multiclass problems in scikit-learn, we can specify the averaging method via the average parameter inside the different scoring functions that we import from the sklean.metrics module, for example, the precision_score or make_scorer functions

* Transforming words into feature vectorsTo construct a bag-of-words model based on the word counts in the respective documents, we can use the CountVectorizer class implemented in scikit-learn. As we will see in the following code section, the CountVectorizer class takes an array of text data, which can be documents or just sentences, and constructs the bag-of-words model for us:

* Naive Bayes is a linear classifier, while KNN is not. The curse of dimensionality and large feature sets are a problem for KNN, while Naive Bayes performs well. KNN requires no training (just load in the dataset), whereas Naive Bayes does.

* The McNemar test, introduced by Quinn McNemar in 1947 (McNemar 1947), is a non-parametric statistical test for paired comparisons that can be applied to compare the performance of two machine learning classifiers. Cochran’s Q Test  or F Test for >2.

* [Model Comparison](http://hunch.net/?p=224)

### Model Explanability

Use SHAP.

## Supervised

General format: Intro, Assumptions, Evaluation, Interpretation, Pros/Cons, Notes

### GLM

####`Linear Regression

add interaction terms

https://scikit-learn.org/stable/modules/generated/sklearn.gaussian_process.GaussianProcessRegressor.html#sklearn.gaussian_process.GaussianProcessRegressor

Discuss Ridge, Lasso, and Elastic Net here.

Poisson: When you’re predicting a count value. (How many dogs will I see in the park?)

Poisson Regression: The Poisson distribution is used to model variation in count data (that is, data that can equal 0,1,2,...).

Remember that you must specify family = poisson or family = quasipoisson when using glm() to fit a count model.

One of the assumptions of Poisson regression to predict counts is that the event you are counting is Poisson distributed: the average count per unit time is the same as the variance of the count. In practice, "the same" means that the mean and the variance should be of a similar order of magnitude.

When the variance is much larger than the mean, the Poisson assumption doesn't apply, and one solution is to use quasipoisson regression, which does not assume that variance=meanvariance=mean.

Ridge/Lasso:

Minimizes RSS but also has shrinkage penalty (L2 penalty). A small lambda penalizes the RSS more than the shrinkage penalty. A large lambda penalizes the shrinkage penalty more than the RSS. By shrinking the coefficient estimates towards 0 by increasing lambda, the bias increases slightly but remains relatively small, the variance reduces substantially, and the mean squared error of the predictions drops. Not scale invariant due to the shrinkage penalty. To avoid the issue of overvaluing or undervaluing certain predictor variables simply based on their magnitudes, we must standardize the variables prior to performing ridge regression. The main disadvantage of ridge regression is that, while parameter estimates are shrunken, they only asymptotically approach 0 as we increase the value of lambda. 

Standardize for ridge/lasso alpha makes them not scale invariant

Minimizes RSS but also has L1 penalty (norm). This necessarily forcessome coefficient estimates to be exactly 0 (when lambda is sufficiently large). It has the added advantage of essentially performing variable selection, yielding models that are both accurate and parsimonious. Restricting ourselves to simpler models by including a Lasso penalty will generally decrease the variance of the fits at the cost of higher bias.

Note: In both ridge and lasso regression, is important to select an appropriate value of lambda by means of cross-validation.

Quantile Regression models the median while Linear Regression models the mean

Linear Regression - BLUE: Best Linear Unbiased (average amount wrong by is error) Estimator

The standard least squares coefficient estimates are scale equivariant: if we multiply a predictor variable by a constant, the corresponding least squares coefficient estimate will be scaled down by the same constant. Used when you’re predicting a continuous value. In regression, it is often recommended to center the variables so that the predictors have mean 0. This makes it so the intercept term is interpreted as the expected value of Y_i when the predictor values are set to their means. Otherwise, the intercept is interpreted as the expected value of Y_i when the predictors are set to 0, which may not be a realistic or interpretable situation. When p > n, we can no longer calculate a unique least square coefficient estimate, the variances become infinite, so OLS cannot be used at all.

* In presence of few variables with medium / large sized effect, use lasso regression. In presence of many variables with small / medium sized effect, use ridge regression.

* The fitted regression line using a sample of data gives imperfect predictions for future observations due to sampling variability and randomness in Y that is not related to X.

* Linear Correlation => Causation if covariates respect: linearity normality indep homoscedasticity + all confounders in model

* In summary, "pooling" your data and fitting one combined regression function allows you to easily and efficiently answer research questions concerning the binary predictor variable.

* If two independent variables are measured in exactly the same units, we can asses their relative importance in their effect on y quite simply: the larger the coefficient, the stronger the effect.

* Okay, so many of the features are strongly correlated. We can make use of this in our model by including polynomial features (e.g. PolynomialFeatures(degree=2) from scikit-learn). Adding these brings our validation loss down to 0.69256 (-0.05% from baseline).

* We prefer natural logs (that is, logarithms base e) because, as described above, coefficients on the natural-log scale are directly interpretable as approximate proportional differences: with a coefficient of 0.06, a difference of 1 in x corresponds to an approximate 6% difference in y, and so forth.

The regression assumption that is generally least important is that the errors are normally distributed. In fact, for the purpose of estimating the regression line (as compared to predicting individual data points), the assumption of normality is barely important at all. Thus, in contrast to many regression textbooks, we do not recommend diagnostics of the normality of regression residuals. [Gelman]

Linear regression errors are not autocorrelated. The Durbin-Watson statistic detects this; if it is close to 2, there is no autocorrelation.

A linear regression model is only as good as the validity of its assumptions, which can be summarized as: $y = b_0+b_1x + \epsilon$, $\epsilon$ is i.i.d from N(0, $\sigma$). More verbosely:

* Linearity: This is a linear relationship between the predictor and the response variables. If this relationship is not clearly present, transformations (log, polynomial, exponent and so on) of the X or Y may solve the problem. Check with a scatterplot.

* Normality: The error terms are drawn from an identical Gaussian distribution, i.e a normal distribution of the dependent variable for each value of the independent variable. Inspect the quantile-quantile plot of the residuals. Also Shapiro-Wilk Test for Normality.

* Non-correlation or independence of errors: A common problem in the time series and panel data where en = betan-1; if the errors are correlated, you run the risk of creating a poorly specified model. The residual value for an arbitrary observation is not predictable from knowledge of another observation’s residual value; they are uncorrelated.  Inspect the residual plot after fitting the regression. Ideally, there would be no clear pattern in the fluctuation of the error terms.

* Homoscedasticity (constant variance): Normally the distributed and constant variance of errors, which means that the variance of the errors is constant across the different values of inputs. Violations of this assumption can create biased coefficient estimates, leading to statistical tests for significance that can be either too high or too low. This, in turn, leads to the wrong conclusion. This violation is referred to as heteroscedasticity.  The error terms have the same variance. Check the residual plot which is a scatterplot of the residuals vs the fitted values.

* No multi-colinearity: No linear relationship between two predictor variables, which is to say that there should be no correlation between the features. This, again, can lead to biased estimates. If not coefficient estimates could be unstable, introduce redundancies within predictors, and make it more difficult to make inferences. Could inflate standard errors, decrease power and reliability of regression coefficients, and create need for a larger sample size. Check the variance inflation factors. Tells the factor by which the estimated variance of a variable is larger in comparison ti it it were completely uncorrelated with other variables in the model. If the VIF is more than five then the variable is a candidate to remove from the model. Its information is contained in the other variables. Variance Inflation Factor: MEasures how the model facotrs influence hte uncertainity of coefficient estimates. >=5 is bad.

* Minimal outliers: Outliers can severely skew the estimation and, ideally, must be removed prior to fitting a model using linear regression; this again can lead to a biased estimate.

A practical [summary](http://www.statmethods.net/stats/rdiagnostics.html) using R. 

```{r, eval = F}
# general check
plot(rgr_lr_st1)

# linearity check
avPlots(rgr_lr_st1)

# repeat of outlier analysis
#influencePlot(rgr_lr_st1)

# multi-colinearity
vif(model) %>% data.frame() %>% mutate(VIF = `GVIF..1..2.Df..`, VIF = VIF^2)

# Test for Autocorrelated Errors
durbinWatsonTest(rgr_lr_st1)

data = rnorm(100) # Generating data from a standard normal distribution.
shapiro.test(data) # P-value insignificant; retain H0, conclude data is normally distributed.

# Inspect this same data using the QQ-plots (For normal data, the QQ-plot produces a straight-line relationship. For uniform data, the QQ-plot does NOT produce a straight-line relationship): 
qqnorm(normal.data) + qqline(normal.data)
#Breusch-Pagan (BP) test lmtest package: is used to test for heteroskedasticity in a linear regression model
```

Outliers are observations that have high residual values. Leverage points are observations that have unusually small or large independent variable values. Cook's distance helps to measure the effect of deleting an observation from the #dataset and rerunning the regression. Observations that have large residual values and also high leverage tend to pose threats to the accuracy of the regression line and thus need to be further investigated. Look at influence plot. Confidence and prediction intervals. For avplot distinct patterns are indications of good contributions. Influence plot to look at hat values (lower is better). Use F-test to compare models. F-test & partial f-testr for simple and multiple linear regression.

```{python, eval = F}
statsmodels.stats.outliers_influence.variance_inflation_factor
```

Fixing assumptions:

Transformations: Can remedy assumption violations and strengthen linear relationships between variables, but can lead to overfitting and less interpretability. square root correction: Take square root of x variable(s). log transformation: Take log of y. General rule of thumb: powers > 1 for skewed left data, powers < 1 for data skewed right.

Box-Cox: Iterates along values of lambda by maximum likelihood so as to maximize the fit of the transformed variable to a normal distribution. Does not guarantee normality since it minimizes standard deviation. Can only be used on positive values. Use on negative values by shifting by a constant value. Use Box-Cox transformations when predictions are skewed.

* Forward and Backward Stepwise Selection.

* For simple linear regression, the principal hypothesis test is as follows: H_0 : ? 1 = 0, H_A: ? 1 ≠ 0.
If H_0 is true then the population mean of Y would be ? 0 no matter what the value of X. (X has no effect on Y.) 

* F-Test: H_0 says that all/some coefficients are zero versus H_a which says that there is at least one non-zero coefficient. If h0 fail to reject than F value close to 1, else F value greater than 1. 

* A.I.C and B.I.C: Smaller values are better. Can be used to compare multiple models at the same time. They reward goodness of fit and penalizes complexity. Favor A.I.C for prediction and B.I.C for descriptive power (penalty term more stringest and favors a parsimonious model)

* R-squared increases whenever a predictor is added, and it doesn't take model complexity into consideration which makes it prone to overfitting. Use adjusted R-squared instead. Additional predictors only make this increase is they are statistically significant. It’s easy to show that given no other data for a set of numbers, the predictor that minimises the MAE is the median, while the predictor that minimises the MSE is the mean. 

* Compare RSME to sd of data for sense of how good it is. (If RSME < sd then good.)

**Pros**

* Very fast (runs in constant time)

* Easy to understand the model

* Less prone to overfitting

**Cons**

* Unable to model complex relationships

* Unable to capture nonlinear relationships without first transforming the inputs

https://www.rdocumentation.org/packages/GGally/versions/1.4.0/topics/ggcoef

https://cran.r-project.org/web/packages/jtools/vignettes/summ.html

* https://twitter.com/alexpghayes/status/1033824995905077250

* [Quantile regression](https://en.wikipedia.org/wiki/Quantile_regression) is an alternative for quantiles.

* Type 1 Error: Accept ha when h0 is true.

* RSS is The sum of the squared error terms for each observation in our dataset. RSE is The standard deviation of the residuals about the regression surface and is an estimate of sigma. TSS is a measure of the total squared deviation of our response variable from its mean value. R^2 = 1 – RSS/TSS.

* Increasing x1 by 1 means you are increasing the underlying X1 by 1 standard deviation x1+1=(X1+sig-mu)/sig. Therefore you can say that b1 is the effect on y of increasing X1 by 1 sigma.

* If there is an ascending or descending order to your dependent variable, ordinal regression is more appropriate as it has more power than multinomial logistic regression.

* leaps lm package r is a greedy way to find the best predictors by cycling through all the combinations.

* Linear Regression by Year

```{r, eval = FALSE}
library(purrr)
pga %>% 
  select(name,year,driveavg,drivepct, score.avg) %>%
  split(.$year) %>%
  map(~lm(score.avg ~ driveavg + drivepct, data=.)) %>%
  map(summary)
```

The importance of a feature in a linear regression model can be measured by the absolute value of
its t-statistic. The t-statistic is the estimated weight scaled with its standard error.

effect of linear regression is w_ix_i. A feature effect plot shows the distribution of effects throughout the data.

## Logistic Regression

logistic is the same as probit

wilkinson rogers logistic regression 

weighted logistic regression

The right-hand predictor side of the equation must be linear with the left-hand outcome side of the equation. You must test for linearity in the logit (in logistic regression the logit is the outcome side). This is commonly done with the Box-Tidwell Transformation (Test): Add to the logistic model interaction terms which are the crossproduct of each independent times its natural logarithm [(X)ln(X)]. If these terms are significant, then there is nonlinearity in the logit. This method is not sensitive to small nonlinearities.

Logistic regression assumes that logit(y) is linear in the values of x. Like linear regression, logistic regression will find the best coefficients to predict y, including finding advantageous combinations and cancellations when the inputs are correlated. In other words, you can think of logistic regression as a linear regression that finds the log-odds of the probability that you’re interested in. Logistic Regression can also be used with kernel methods.

Logistic: When you’re predicting which category your observation is in. (Is this is a cat or a dog?)

The link function is the logit function. Logit is the inverse of the sigmoid and gives the log odds, i.e p/(1-p).

Easy to incorpotate prior knowledge, number fo features are small, training is fast, precision not critical. 

No closed form expression to maximize coefficients with maximum likelihood estimation, so one uses gradient descent or stochastic gradient descent. The second one is faster. 

For logistic regression value of c penalizes features. Low c penalizes a lot and vice versa. A large c decreases the effect of the regularization term (the l2 penalization). 

Makes a linear boundary between classes. 

For multiclass classification it will build multiple models. Given 3 classes 0,1, and 2, there will be models 0 and not 0, 1 and not 1, and 2 and not 2.

Standardization isn't required for logistic regression. The main goal of standardizing features is to help convergence of the technique used for optimization. For example, if you use Newton-Raphson to maximize the likelihood, standardizing the features makes the convergence faster. Otherwise, you can run your logistic regression without any standardization treatment on the features.

* The linear regression analysis requires all variables to be multivariate normal.  This assumption can best be checked with a histogram or a Q-Q-Plot. 

* Requires the dependent variable to be binary and ordinal logistic regression requires the dependent variable to be ordinal.

* The observations to be independent of each other. In other words, the observations should not come from repeated measurements or matched data.

* There to be little or no multicollinearity among the independent variables.

* Assumes linearity of independent variables and logit of the probabilities (logit(p) = log(p/(1-p))). Check [in R](https://stats.stackexchange.com/questions/169348/how-should-i-check-the-assumption-of-linearity-to-the-logit-for-the-continuous-i).

* There is no influential values (extreme values or outliers) in the continuous predictors

Notice the points fall along a line in the middle of the graph, but curve off in the extremities. Normal Q-Q plots that exhibit this behavior usually mean your data have more extreme values than would be expected if they truly came from a Normal distribution.

The Durbin-Watson test is used to test the null hypothesis that linear regression residuals are uncorrelated, against the alternative that autocorrelation exists

https://data.library.virginia.edu/diagnostic-plots/

**No Multicolinearity**

`multicol` shows which columns could be removed for multi-collinearity. (The vif is not working because of multicolinearity.)

```{r, eval = F}
# vif(clf_lr$finalModel)
# multicol <- alias(clf_lr$finalModel)$Complete
# multicol
```

**Linear With The Logit Of Predictions**

```{r, eval = F}
# box tidwell doesn't work since features have negative values.

# min_max_scaler <- function(x) (x - min(x))/(max(x) - min(x))
# 
# df_num_selected <- df2 %>% 
#   select(
#     OverallMap,
#     StrandMap,
#     lesson_length,
#     g_avg_overall_map,
#     g_avg_strand_map,
#     g_avg_score,
#     g_num_students,
#     cohort_avg_overall_map,
#     cohort_avg_strand_map
#   ) %>%
#   map(min_max_scaler) %>% 
#   data.frame() %>% 
# 
# formula_all_num_features <- as.formula(glue('pass ~ {paste(df_num_selected %>% names, collapse = " + ")}'))
# car::boxTidwell(formula_all_num_features, data = df_num_selected )

# Visual test too many features to work well

# lin_test <- df2 %>%
#   dplyr::select_if(is.numeric) 
# 
# predictors <- colnames(lin_test)
# 
# lin_test <- lin_test %>%
#   mutate(logit = log(clf_lr_final$fitted.values/(1-clf_lr_final$fitted.values))) %>%
#   gather(key = "predictors", value = "predictor.value", -logit)
# 
# ggplot(lin_test, aes(logit, predictor.value))+
#   geom_point(size = 0.5, alpha = 0.5) +
#   geom_smooth(method = "loess") + 
#   theme_bw() + 
#   facet_wrap(~predictors, scales = "free_y")
```

* Wald Test: h_0: b = 0 and h_a: b =/= 0. h_0 means the log odds are unaffected by x and so x has no bearing on the prediction of success.

* Deviance G^2 and Goodness of Fit: The deviance associated with a given logistic regression model M is based on comparing the maximum log-likelihood of model M against the saturated model S. The smaller the deviance the better. For goodness of fit h0 says the model is appropriate while H_a says the opposite.

* McFadden's Pseudo R^2. 

* A.I.C / B.I.C

* Absolute scale odds instead of relative

**Pros**

* Highly interpretably

* Model training and prediction are fast

* No tuning outside of regularization required

* Features don't need scaling

* Can perform with a small number of observations

* Outputs well-calibrated predicted probabilities

* low variance

**Cons**

* Presumes a linear relationship between the features and the log-odds of the response.

* Performance is generally not competitive with the best supervised learning methods

* Can't automatically learn feature interactions

* Breaks down when classes are perfectly separable.

* High bias

with bayesian log reg you can have a probability distribution of the probability estimate so you can attach a ci to the prediction

## Generalized Additive Models

### Intro

mgcv::gam: More complex than lm, more likely to overfit, best used on larger data sets. use s(var) to denote non-linear relationship. Don't use s() with categorical variable. Use type = terms for y values of plots to get predictions type = response. 

Also remember that gam() from the package mgcv has the calling interface

gam(formula, family, data)
For standard regression, use family = gaussian (the default).

For GAM models, the predict() method returns a matrix, so use as.numeric() to convert the matrix to a vector.

### Assumptions

### Evaluation

### Pros/Cons

**Pros**

**Cons**

## K-Means Clustering [US]

### Intro

K-Means clustering method considers two assumptions regarding the clusters – first that the clusters are spherical and second that the clusters are of similar size.

k-means assumes the variance of the distribution of each attribute (variable) is spherical;
all variables have the same variance;

the prior probability for all k clusters is the same, i.e., each cluster has roughly equal number of observations;

Must choose k for clusters. Initialize cluster centes randomly, assign each point to its closest cluster by a distance metric. Recalculate centroids. Halt when cluster assignments no longer change. Clusters will be distinct and non-overlapping. 

Goal to minimize within-cluster variation. The within-cluster variation for the kth cluster is the sum of all of the pairwise squared Euclidean distances between the observations in the kth cluster divided by the total number of observations in the kth cluster. Limitation is that it depends on initialization of centroids. Guaranteed convergence but only to a local minima. Run the algorithm several times and pick the solution that yields the smallest within-cluster variance. Increasing k will decrease variance and increase bias and vice versa. K-means: Jaccard coefficient.

Note: Not enough to use within-cluster variance as this decreases as one increases k. Use elbow method or scree plot to choose optimal k where the variance no longer decreases dramatically. To choose how many groups to use, I ran a k-means analysis for each possible number of groups from 5 to 35 and found that 20 was right about the spot that the amount of variance stopped decreasing consistently. This is called the elbow test and while the results weren’t totally definitive, they fit in well with the general rule of thumb for determining # of groups which is the square root of the # of observations/2.

One way to assess whether a cluster represents true structure is to see if the cluster holds up under plausible variations
in the dataset. The fpc package has a function called clusterboot() that uses bootstrap resampling to evaluate how stable a given cluster is.[3] clusterboot() is an integrated function that both performs the clustering and evaluates the final produced clusters. It has interfaces to a number of R clustering algorithms, including both hclust and kmeans.

In K-means, we assume that each cluster fits a Gaussian distribution (normal distribution)

We can set K to optimally cluster the data by starting with a small number of clusters, and then iteratively splitting them until all clusters fit a normal distribution.

Davies–Bouldin index: This is an internal evaluation scheme, where the validation of how well the clustering has been done is made using quantities and features inherent to the dataset. This has a drawback that a good value reported by this method does not imply the best information retrieval. 

**Pros** 

Uses simple principle which can be explained in non-statistical terms. It is efficient.

**Cons**

Less sophisticated, random choices of centers, and requires guess for centers.

## Hierarchical Clustering

Generates dendrograms. The lower down a fusion occurs the more similar the group of observations and vice versa. Begin with n observations and a distance measure of all pairwise dissimialirities. Evaluate pairwise intercluster dissimiliarities among the clusters and fuse pair of clusters that are least dissimilar. Repeat process for remaining clusters. Continue for i=n to i=2. 
Need to pick a dissimilarity measure and a linkage method. Complete linkage: maximal inter-cluster dissimilarity, single linkage: minimal inter-cluster dissimilarity, avergae linkage: mean inter-cluster dissimilarity. Complete is sensitive to outliers but tends to produce compact clusters. Distance between groups: complete, average, and ward. Single not as sensitive to outliers but susceptible to chaining effect where clusters can often not represent intuitive groups. Average strikes a balance between the two. Usually standardize data before clustering. Sklearn.metrics has pairwise distances.

K-Means vs Hierarchical Clustering: K-means clustering needs the number of clusters to be speciﬁed. Hierarchical clustering doesn’t need the number of clusters to be speciﬁed. K-means clustering is usually more effcient run-time wise.

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

## PCA

### Intro

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

* Center and scale data. The eigenvectors yield orthogonal directions of greatest variability(principal components). The eigenvalues correspond to the magnitude of variancealong the principal components. Interpretability is a negative. PCA is completely nonparametric: any data set can be plugged in and an answer comes out, requiring no parameters to tweak and no regard for how the data was recorded. From one perspective, the fact that PCA is non-parametric (or plug-and-play) can be considered a positive feature because the answer is unique and independent of the user. From another perspective the fact that PCA is agnostic to the source of the data is also a weakness. When using dimensional reduction we restrict ourselves to simpler models. Thus, we expect bias to increase and variance to decrease. Getting latent components. Visualize high dimensional data. Reduce noise. Preprocessing. scale and center data before doing. Needs regularization. Too many principal components F1 score starts to drop after increase. Best F1 is 1. set number of components. Use fit_transforms, use explained_variance_ratio_ to see how much of the variance is explained by each component. Choose features that explain most of the variances, then use a inverse_transform to reconstruct your x. Minimum number of principal components is min(n,p).

* pca: It accounts for as much of the variability in the data as possible by considering highly correlated features. Each succeeding component in turn has the highest variance using the features that are less correlated with the first principal component and that are orthogonal to the preceding component.

### Other

* 1) look at variance: apply(USArrests , 2, var) | 2) pca & scale: pca = prcomp(USArrests , scale = TRUE) | 3) plot: biplot(pca, scale = 0)

* pca$rotation contains the principal component loadings matrix which explains proportion of each variable along each principal component.

* Kaiser-Harris criterion suggests retaining PCs with eigenvalues > 1; PCs with eigenvalues < 1 explain less variance than contained in a single variable. Cattell Scree test visually inspects the elbow graph for diminishing return; retain PCs before a drastic drop-off.

PC columns contain loadings; correlations of the observed variables with the Pcs. h2 column displays the component comunalities; amount of variance explained by the components.

Note: Look at factorplot. Shows pot of relationship between variables and principal components.

It is also possible to decompress the reduced dataset back to 784 dimensions by applying the inverse transformation of the PCA projection. Of course this won’t give you back the original data, since the projection lost a bit of information (within the 5% variance that was dropped), but it will likely be quite close to the original data. The mean squared distance between the original data and the reconstructed data (compressed and then decompressed) is called the reconstruction error.

It turns out that many things behave very differently in high-dimensional space. For example, if you pick a random point in a unit square (a 1 × 1 square), it will have only about a 0.4% chance of being located less than 0.001 from a border (in other words, it is very unlikely that a random point will be “extreme” along any dimension). But in a 10,000-dimensional unit hypercube (a 1 × 1 × ⋯ × 1 cube, with ten thousand 1s), this probability is greater than 99.999999%. Most points in a high-dimensional hypercube are very close to the border.

Before looking at the PCA algorithm for dimensionality reduction in more detail, let's summarize the approach in a few simple steps:
Standardize the -dimensional dataset.

Construct the covariance matrix.Decompose the covariance matrix into its eigenvectors and eigenvalues.
Select  eigenvectors that correspond to the  largest eigenvalues, where  is the dimensionality of the new feature subspace ().

Construct a projection matrix  from the ""top""  eigenvectors.

Transform the -dimensional input dataset  using the projection matrix  to obtain the new -dimensional feature subspace.

Probabilistic PCA introduces the Gaussian distribution to the PCA modeling framework.

Kernel PCA must project data into a higher dimensional space than that of the original data.

## KNN

### Intro

Calculate distance between each observation and all the others. Determine the k nearest observations to the observation. Classify the observation as the most frequent class of the k nearest observations. Small k's are not robust to outliers, highlight local variations and induce unstable decision boundaries. Large k's are robust to outliers, highlight global variations and induce stable decision boundaries. Good value to choose is k = sqrt(n). Can use maximum prior probability to decide ties. Use Euclidean distance for numerical data and Hamming distance for categorical data. Latter treats dimensions equally and is symmetric. Low k is low bias, high variance and high k is high bias low variance. 1NN can't adapt to outliers and has no notion of class frequencies. Can use weighted KNN. Easy in sklearn.

curse of dimensionality, overfitting, correlated features, cost to update, sensitivity of distance metrics

smaller k means smaller training error, ut larger k is more stable. 

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

**Pros**

Only assumption is proximity. Non-parametric.

 The only assumption we are making about our data is related to proximity (i.
e., observations that are close by in the feature space are similar to each
other in respect to the target value).
 We do not have to fit a model to the data since this is a non-parametric
approach.

- Powerful
- No training involved (“lazy”)
- Naturally handles multiclass classification and regression

What is a common drawback of 3NN classifiers? Prediction on large data sets is slow.

**Cons**

Have to decide k and distance metric. Can be sensitive to outliers or irrelevant attributes. Computationally expensive.

knn is terrible with high dimensions. Bad with categorical data.

 Expensive and slow to predict new instances
- Must define a meaningful distance function
- Performs poorly on high-dimensionality datasets

We have to decide on K and a distance metric.

Can be sensitive to outliers or irrelevant attributes because they add noise.

Computationally expensive; as the number of observations, dimensions, and K increases, the time it takes for the algorithm to run and the space it takes to store the computations increases dramatically.


##SVM

### Intro

Selection of margin in SVM is a convex optimization problem. What is the objective of the maximum margin approach?  To ensure small prediction error when the underlying distribution is not known

The LinearSVC class regularizes the bias term, so you should center the training set first by subtracting its mean. This is automatic if you scale the data using the StandardScaler. Moreover, make sure you set the loss hyperparameter to "hinge", as it is not the default value. Finally, for better performance you should set the dual hyperparameter to False, unless there are more features than training instances (we will discuss duality later in the chapter).

With so many kernels to choose from, how can you decide which one to use? As a rule of thumb, you should always try the linear kernel first (remember that LinearSVC is much faster than SVC(kernel="linear")), especially if the training set is very large or if it has plenty of features. If the training set is not too large, you should try the Gaussian RBF kernel as well; it works well in most cases. Then if you have spare time and computing power, you can also experiment with a few other kernels using cross-validation and grid search, especially if there are kernels specialized for your training set’s data structure.

Here mostly talking about a maximal margin classifier. A separating hyperline of data of two classes. Maximizes distance to the nearest point in either class, i.e, the margin. Points which delineate the boundary are called support vectors. Correct classification first and then maximizing the margin. SVM only really works well with linear hyperplanes. The c hyperparameter deals with the tradeoff between a smooth decision boundary and correct classification. The larger the c the more points classified correctly as it increases the penalty for wrong classification. A smaller c gives more room for intial error which helps improve accuracy for not easily separable data. Work well in complicated domains with clear line of separation. Not so well in for large datasets because of training and not when there is a lot of noise. Can solve nonlinear decision boundaries by using polynomial terms. Kernel trick that draws boundaries by looking into higher dimensions. 

Extracting the coefficients from the hyperplane equation (not including the intercept) yields what is called a normal vector. This vector points in a direction orthogonal to the surface of the hyperplane and essentially defines its orientation.

Big data set and lot of features SVM might be slow and prone to overfitting. SVM slower than naïve bayes. A kernelis a function that quantifies the similarity of two observations. The beauty of the "kernel trick" is that, even if there is an infinite-dimensional basis, we need only look at the n^2 inner products between training data points. SVM not scale invariant. Check if library normalizes by default. RBF kernel is a good default. Try exponential sequences for parameters.

Extension of above info about relaxing margin. Doesn't perfectly separate classes but is more robust to outliers. Helps better classify obervations. Take a penalty by potentially misclassifying soe observations. Have better predictive power. Called a soft margin. The C parameter is the budget for the slack variables which tell where observations are relative to the margin and hyperplane. Only observations that either fall on the margin or violate the margin affect the solution to the optimization problem. More robust than SVM. 

When the support vector classifier is combined with a non-linear kernel, the resulting classifier is called a support vector machine.

Note: Important to make sure the normal vector is of unit length. For the radial kernel, suppose we have a test observation. If it is far from a training observation, the Euclidean distance will be large, but the value of the radial kernel will be small. using kernels is much more computationally efficientbecause we only need to compute the kernel for distinct pairs of observations in our dataset. Furthermore, we need not actually work in the enlarged feature space. Intuitively, the gamma parameter defines how far the influence of a single training example reaches, with low values meaning ‘far’ and high values meaning ‘close’. The gamma parameters can be seen as the inverse of the radius of influence of samples selected by the model as support vectors. 

Multiclass

1v1: Construct a support vector machine for each pair of categories. For each classifier, record the prediction for each observation. Have the classifiers vote on the prediction for each observation.

1vAll: Construct a support vector machine for each individual category against all other categories combined. Assign the observation to the classifier with the largest function value.

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

**Pros**

* Performs similarly to logistic regression when linear separation

* Performs well with non-linear boundary depending on the kernel used

* Handle high dimensional data well

* Can model complex, nonlinear relationships

* Robust to noise (because they maximize margins)

**Cons**

* Susceptible to overfitting/training issues depending on kernel

* Need to select a good kernel function

* Model parameters are difficult to interpret

* Sometimes numerical stability problems

* Requires significant memory and processing power

## Decision Tree

### Intro

So should you use Gini impurity or entropy? The truth is, most of the time it does not make a big difference: they lead to similar trees. Gini impurity is slightly faster to compute, so it is a good default. However, when they differ, Gini impurity tends to isolate the most frequent class in its own branch of the tree, while entropy tends to produce slightly more balanced trees.

Decision Trees make very few assumptions about the training data (as opposed to linear models, which obviously assume that the data is linear, for example). Such a model is often called a nonparametric model, not because it does not have any parameters (it often has a lot) but because the number of parameters is not determined prior to training, so the model structure is free to stick closely to the data.

More generally, the main issue with Decision Trees is that they are very sensitive to small variations in the training data. For example, if you just remove the widest Iris-Versicolor from the iris training set (the one with petals 4.8 cm long and 1.8 cm wide) and train a new Decision Tree, you may get the model represented in Figure 6-8. As you can see, it looks very different from the previous Decision Tree (Figure 6-2). Actually, since the training algorithm used by Scikit-Learn is stochastic6 you may get very different models even on the same training data (unless you set the random_state hyperparameter).

Construct solutions that stratify the feature space into relatively easy to describe regions. Partition predictor space into rectangular or box-like regions. For regression predict the meant of the reponse variables in each region for the training observations in that space. Top down and greedy approach called recursive binary spltting to find ebst solution. Greedy because splits based on best result. The recursive binary splitting process depends on the greatest reduction in the RSS. Entropy very important. Decides where tree splits. Measure of impurity in examples. Entropy between 0 and 1. 0 means no impurity. Maximial is 1 when there is an even split between options. Key term: information gain. Decisions tree maximize this. Easy to interpret, prone to overfitting. 
Where each data point has its own node, the variance is high and the training error is 0.  Deciding on the number of splits prior to building a tree isn’t the best strategy. The best subtree will be the one that yields the lowest test error rate. Given a subtree, we can estimate the test error by implementing the crossvalidationprocess, but this is too cumbersome because the large number of possible subtrees. The tuning parameter alpha helps balance the tradeoff between the overall complexity of the tree and its fit to the training data. Small values of alpha yield trees that are quite extensive (have many terminal nodes). Large values of alpha yield trees that are quite limited (have few terminal nodes). Similar to ridge/lasso regression. Ultimately, the subtree that is used for prediction is built using all of the available data with the determined optimal value of alpha.

Regression: Use cost complexity pruning to build set of subtrees as a function of lambda. Classification: Use Gini index, measures total variance among classes. 

Note: Duplicate splits happen when they increase node purity. While pruning reduces the variance of the overall tree model upon repeated builds with different datasets, we induce biasbecause the trees are much simpler.

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

**Pros**

* Fast

* Robust to noise and missing values

* Accurate

**Cons**

* Weak predictive accuracy and prone to overfitting.

* Complex trees are hard to interpret

* Duplication within the same sub-tree is possible

## Bagging

### Intro

used to decrease variance in decision trees

How it works: train multiple trees using bootstrapped datasets, regression trees: average the predictions from all the trees, classification: take a majority vote of the predictions, majority vote: the class which occurs most frequently, Out of bag (OOB) error, Only a portion of the data is used to train each tree, The remaining data which wasn't selected can be used  to assess the tree's performance, (the response for each observation is predicted using
only the trees that were not fit using that observation)

Bagging involves randomly generating Bootstrap samples from the dataset and trains the models individually. Predictions are then made by aggregating or averaging all the response variables:For example, consider a dataset (Xi, Yi), where i=1 …n, contains n data points.Now, randomly select B samples with replacements from the original dataset using Bootstrap technique.Next, train the B samples with regression/classification models independently. Then, predictions are made on the test set by averaging the responses from all the B models generated in the case of regression. Alternatively, the most often occurring class among B samples is generated in the case of classification.

Bagging stabilizes decision trees and improves accuracy by reducing variance.
            
Bagging reduces generalization error.

Take repeated samples of the same size from the single overall training dataset. Treat these different sets of data as pseudo-training sets. Fitting separate, independent decision treesto each of the bootstrapped training data sets. We can then average all predictions (or take the majority vote) to obtain the bagged estimate. Instead of pruning back our trees, create very large trees in the first place. These large trees will tend to have low bias, but high variance. Retain the low bias, but get rid of the high variance by averaging. Con is that the trees are correlation. 
train multiple trees using bootstrapped data to reduce variance and prevent overfitting 

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

**Pros**

* reduces variance in comparison to regular decision trees

* Can provide variable importance measures: classification: Gini index + regression: RSS

* Can easily handle qualitative (categorical) features

* Out of bag (OOB) estimates can be used for model validation

**Cons**

* Not as easy to visually interpret

* Does not reduce variance if the features are correlated

## Random Forest

### Intro

Build a number of decision trees using bootstrapped samples

At each split in the tree only a portion of the features are considered

a feature is selected from a subset of features not the whole feature space

the subset is usually sqrt(n.features)

This allows trees to be built without some of the strong features decorrelates the trees, unlike bagging

Random forests are improvised supervised algorithms than bootstrap aggregation or bagging methods, though they are built on a similar approach. Unlike selecting all the variables in all the B samples generated using the Bootstrap technique in bagging, we select only a few predictor variables randomly from the total variables for each of the B samples. Then, these samples are trained with the models. Predictions are made by averaging the result of each model. The number of predictors in each sample is decided using the formula m = √p, where p is the total variable count in the original dataset.Here are some key notes:This approach removes the condition of dependency of strong predictors in the dataset as we intentionally select fewer variables.

Draw a random bootstrap sample of size n (randomly choose n samples from the training set with replacement).Grow a decision tree from the bootstrap sample. At each node:Randomly select d features without replacement.Split the node using the feature that provides the best split according to the objective function, for instance, by maximizing the information gain.Repeat the steps 1 to 2 k times.Aggregate the prediction by each tree to assign the class label by majority vote. Majority voting will be discussed in more detail in Chapter 7, Combining Different Models for Ensemble Learning.

Random forests further improve decision tree performance by de-correlating the individual trees in the bagging ensemble.

Random forests decorrelate tree it generates and thus results in a reduction in variance. Similar to bagging, we first build various decision trees on bootstrapped training samples, but we split internal nodes in a special way. Each time a split is considered within the construction of a decision tree, only a random subset of ᬊthe overall predictors are allowed to be candidates. At every split, a new subset of predictors is randomly selected. The random forest procedure forces the decision tree building process to use different predictors to split at different times. Should a good predictor be left out of consideration for some splits, it still has many chances to be consideredin the construction of other splits. We can’t overfit by adding more trees. The variance just ends up decreasing. Out of bag score is a good estimate of the test score and is the non-bootstrapped data. Need to turn on this scoing method.
Error Rate: Depends on correlation between trees (higher is worse), strength of single trees (higher is better). Increasing number of features for each split increases correlation and strength of single trees.

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

**Pros**

Decorrelates trees (relative to boosted trees)

important when dealing with mulitple features which may be correlated

reduced variance (relative to regular trees)

All purpose model that performs well on most problems. Automatically chooses the best features. High accuracy.

**Cons**

Hard to interpret and needs a lot of work to tune parameters.

Not as easy to visually interpret

## Boosting

### Intro

Unlike boosting and random forests, can overfit if number of trees is too large

Similar to bagging, but trees are grown sequentially. Each tree is created using information from previously grown trees 

Each tree is generated using information from previously grown trees; the addition of a new tree improves upon the performance of the previous trees. The trees are now dependentupon one another. Boosting approach tends to slowly learn our data. Given a current decision tree model, we fit a new decision tree to the residualsof the current decision tree. The new decision tree (based on the residuals) is then added to the current decision tree, and the residuals are updated. We limit the number of terminal nodes in order to sequentially fit small trees. By fitting small trees to the residuals, we slowly improve the overall model in areas where it does not perform well. 

Note: Unlike in bagging and random forests, boosting can overfit if ᫦is large (although very slowly). Use cross-validation to select number of trees᫦. Alpha controls the rate at which boosting learns and is usually between 0.01 to 0.001. A small alpha usually goes with a large number of trees. Can also choose the number of splits. Typically using stumps (single splits d = 1) is sufficient and results in an additive model. 

Note on Variable Importance: For regression trees, we can use the reduction in the RSS. For classification trees, we can use the reduction in the Gini index. A relatively large value indicates a notable drop in the RSS or Gini index, and thus a better fit to the data; corresponding variables are relatively important predictors.

Similar to bagging, but learns sequentially and builds off previous trees

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

**Pros**

Somewhat more interpretable than boosted trees/random forest as the user can define the size of each tree resulting in a collection of stumps (1 level) which can be viewed as an additive model

Can easily handle qualitative (categorical) features

**Cons**

## Association Rule Mining

### Intro

* Used in Genetics, Fraud, and Market Basket Analysis, etc. A typical rule might be: if someone buys peanut butter and jelly, then that person is likely to buy bread as well. 

* Tutorial: http://pbpython.com/market-basket-analysis.html

* Incredibly big feature space (2^k-1). 

* The Apriori algorithm employs a simple a priori belief as a guideline for reducing the association rule space. 

* Support: the fraction of which each item appears within the dataset as a whole. Support(item) = count(item)/N. Higher support is better. 

* nfidence: the likelihood that a constructed rule is correct given the items on the left hand side of the transaction. A higher level of confidence implies a higher likelihood that Y appears alongside transactions in which X appears.

* ft: the ratio by which the confidence of a rule exceeds the expected outcome. When lift > 1, the presence of X seems to have increasedthe probability of Y occurring in the transaction. When lift < 1, the presence of X seems to have decreasedthe probability of Y occurring in the transaction. When lift = 1, X and Y are independent.

* t thresholds for support and confidence and then the algorithm goes from all 1-combinations to 2-combinations and up. Those subset below the threshold don't make it to the higher iterations. 

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

**Pros**

* Ideally suited for working with very large amounts of transactional data.

* The results are rules that are generally easy to understand and have a high amount of interpretability. 

* The process is useful for data mining and uncovering unexpected knowledge within a dataset.

**Cons**

* The outcome is usually not interesting when applied to smaller datasets. 

* It is difficult to separate actual insights from common sense notions. 

* The analyst might be compelled to draw spurious conclusions--remember that correlation doesn’t imply causation!

## Naïve Bayes

### Intro

Laplace smoothing/estimator in Naive Bayes: To see why consider the worst case where none of the words in the training sample appear in the test sentence. In this case, under your model we would conclude that the sentence is impossible but it clearly exists creating a contradiction.

Practitioners do use Naive Bayes regularly for ranking, where the actual values of the probabilities are not relevant—only the relative values for examples in the different classes. Another advantage of Naive Bayes is that it is naturally an “incremental learner.” An incremental learner is an induction technique that can update its model one training example at a time. It does not need to reprocess all past training examples when new training data become available.

Document/spam classification is one use. Assumptions are that all the features are equally likely and are all important. Would be computational expensive without these assumptions with having to track all the joint probabilities. Gaussian for continuous variables, Bernoulli for binary input, and Multinomial for binary and more input. Use MLE to estimate parameters for Gaussian. Bernoulli/Multinomial used for spam classification.The Laplace Estimator (usually chosen to be 1) is a corrective measure that adds a small amount of error to each of the counts in the frequency table of words. The addition of error ensures that each resulting probability of each event will necessarily be nonzero, even if the event did not appear in the training data.

Note: In addition, we can use function "partial_fit" to fit on a batch of samples incrementally while we are using. MultinomialNB and Bernoulli NB also support sample weighting. 

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

**Pros**

* It is relatively simple to understand. Training the classifier does not require many observations, and the method also works well with large amounts of data. It is easy to obtain the estimated probabilityfor a classification prediction.

* Computationally fast

* Simple to implement

* Works well with high dimensions

**Cons**

* Relies on independence assumption and will perform badly if this assumption is not met

* While easily attainable, the estimated probabilities are often less reliable than the predicted class labels themselves.

## LDA

### Intro

Before we take a look into the inner workings of LDA in the following subsections, let's summarize the key steps of the LDA approach:

Standardize the -dimensional dataset ( is the number of features).

For each class, compute the -dimensional mean vector.

Construct the between-class scatter matrix  and the within-class scatter matrix .

Compute the eigenvectors and corresponding eigenvalues of the matrix .

Choose the  eigenvectors that correspond to the  largest eigenvalues to construct a -dimensional transformation matrix ; the eigenvectors are the columns of this matrix.

Project the samples onto the new feature subspace using the transformation matrix.

LDA similar to Naive Bayes but doesn't assume variables are independent, assumes that p(x|y) is a multivariate normal distribution, and assumes gaussian distributions for each class share the same covariance matrix. If they don't share the same covariance matrix, then we use Quadratic Discriminant Analysis which assumes each class has its own. 

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

## QDA

### Intro

TBD

### Assumptions

### Characteristics

### Evaluation

### Pros/Cons

## GAMs

Wiggleness affected by smoothing factor (sp) and number of basis functions (k)

gam(y ~ s(x, k = 3), data = df, sp = .1)
gam(y ~ s(x, k = 3), data = df, method = "REML")

Categorical features must be included as factors.

gam(hw.mpg ~ s(weight) + fuel, data = mpg, method = "REML")

A factor smooth interaction fits different models for different categorical vars.

gam(hw.mpg ~ s(weight, by = fuel) + fuel, data = mpg, method = "REML")

Summary:

edf=1 is a straight line

Visualize: 

plot(mod, select = 1, seWithMean = TRUE, shift = coef(mod)[1])

Model Evaluation:

gam.check: Bad if model hasn't converged. Likely due to too many features. Small p-values indicate residuals not randomly distributed which is often due to not enough basis functions. 

first do concurvity(mod, full = T) then do concurvity(mod, full = F). check co-linearity. worst case is bad over 0.8.

interaction b/w x & y: mod2d <- gam(cadmium ~ s(x, y), data = meuse, method = "REML")

vis.gam for visualization

vis.gam(mod2d, view = c("x", "y"), 
        plot.type = "persp", se = 2, theta = 135)

vis.gam(mod2d, view = c("x", "y"), 
        plot.type = "contour", too.far = 0.05)

vis.gam(mod2d, view = c("x", "y"), plot.type = "contour", too.far = .1)

Make plot with 25% extrapolation
vis.gam(mod2d, view = c("x", "y"), 
        plot.type = "contour", too.far = .25)

Overlay data
points(meuse)

Nonlinear Modeling in R with GAMs:

Fit a model with a factor-smooth interaction:
mod_fs <- gam(copper ~ s(dist, landuse, bs = "fs"), data = meuse, method = "REML")

Plot both models making 3D perspective plots:
vis.gam(mod_sep, view = c("dist", "landuse"), plot.type = "persp")

2-way interactions: 2d interaction smooths, categorical-continuous interaction, tensor smooths: allow to model on different scales (space & time)

tensor_mod <- gam(cadmium ~ te(x, y, elev), data = meuse, method = "REML")

Single-variable smooths use s().
Smooths in which multiple variables interact on the same scale also use s().
Smooths that have only interactions, but have multiple lambda terms or scales, use ti().

te() must be used along. if you include s() switch to ti()

classification: 

outputs on the log odds scale

```{r, eval=F}
#Plot with intercept uncertainty
plot(log_mod2, pages = 1, trans = plogis, shift = coef(log_mod2)[1], seWithMean = TRUE)

#log odds scale
predict(mdl, type = "link") 

#probability scale
predict(mdl, type = "response") 

#construct se.fit on log odds scale than transform to probs with plogis
predict(mdl, type = "link", se.fit = T)

#granular for each record on log odds scale
predict(mdl, type = "terms")

# Calculate predictions and errors
predictions <- predict(log_mod2, newdata = new_credit_data, 
                       type = "link", se.fit = TRUE)

# Calculate high and low predictions intervals
high_pred <- predictions$fit + 2*predictions$se.fit
low_pred <- predictions$fit - 2*predictions$se.fit

# Convert intervals to probability scale
high_prob <- plogis(high_pred)
low_prob <- plogis(low_pred)
```

gams work with broom and caret.

## Hierarchical Models

"Across counties, as the average mother's age increases the birth rate decreases while correcting for state-level impacts" BirthRate ~ AverageAgeofMother + (1 | State)

lmerTest 

Analysis of Variance, or ANOVA, can be used to compare two different lmer models and test if one model explains more variability than the other model. We can use this to compare two lmer models. For example, if we wanted to see if Year is important for predicting Crime in Maryland, we can build a null model with only County as a random-effect and a year model that includes Year. 

* One far out suggestion in one of the links is to do PCA and then regress the original variables against the new axis. 

* Account for longitudinal data: random selection of one event from each student, partition cross validation by dates, pca finds major trends hidden within the data

## Other ML

#### NLP

https://mobile.twitter.com/lmthang/status/1050543868041555969

https://gking.harvard.edu/readme

https://web.stanford.edu/~jurafsky/slp3/

https://finetune.indico.io

http://textable.io/

https://pypi.python.org/pypi/tmtoolkit

http://www.structuraltopicmodel.com/

https://blog.insightdatascience.com/how-to-solve-90-of-nlp-problems-a-step-by-step-guide-fda605278e4e

[Kaggle Guide](https://t.co/Zcnd7EJKsn)

[Chat Bots](https://rasa.ai/)

[Doc Similarity](http://brandonrose.org/clustering)

[Vector Embeddings](http://bookworm.benschmidt.org/posts/2015-10-25-Word-Embeddings.html)

Topic Modeling: [1](http://alexperrier.github.io/jekyll/update/2015/09/04/topic-modeling-of-twitter-followers.html) | [2](http://chdoig.github.io/pytexas2015-topic-modeling/#/) | [3](https://www.cs.princeton.edu/~blei/topicmodeling.html)

[qdap](https://trinker.github.io/qdap/vignettes/qdap_vignette.html)

NLP For: [Web Devs](http://blog.algorithmia.com/natural-language-processing-algorithms-web-developers/) | [Bot Makers](https://stanfy.com/blog/advanced-natural-language-processing-tools-for-bot-makers/)

[NLP Intro](http://blog.algorithmia.com/introduction-natural-language-processing-nlp/)

#### Geospatial

https://geocompr.robinlovelace.net/adv-map.html#interactive-maps

https://www.jessesadler.com/post/gis-with-r-intro/

https://uber.github.io/kepler.gl/#/

http://gisquick.org/

https://carto.com/blog/inside/CARTOframes-python-interface-CARTO/

[R Spatial](http://www.rspatial.org/analysis/rst/2-scale_distance.html)

[tilegrams](https://pitchinteractiveinc.github.io/tilegrams/)

[Spatial DA R](https://data.cdrc.ac.uk/tutorial/an-introduction-to-spatial-data-analysis-and-visualisation-in-r)

#### AI

https://www.stateoftheart.ai/

http://airesources.org/

https://alleninstitute.org | http://allenai.org/index.html | http://geometry.allenai.org/ | https://competitions.codalab.org/competitions/20013 | http://www.hbcse.tifr.res.in/jrmcont/notespart1/node27.html

[AI Music Generation](https://www.jukedeck.com)

[AI Acheivements](https://poo.ai/)

[Create With AI](http://createwith.ai/)

[Hod Lipson](http://www.hodlipson.com/)

[Playing Games](http://www.ggp.org/)

[AI 4 Py](https://wiki.python.org/moin/PythonForArtificialIntelligence)
